Network Configuration Synthesis with Abstract Topologies

### 2016-11-08 paper/abstraction/appendix.tex
updating substitution theorem

@@

\begin{thm}
  $con(compile(pol)) = compile(con(pol))$

    We know from the previous theorems and the definition of concretization, we have the following:

    \[ \begin{array}{lll}
       (t_1, PG^A_1, ord^A_1), \dots, (t_k,PG^A_k,ord^A_k)    &=& compile_{ABGP}(pol) \\
       (\Gamma(t1), PG_1, ord_1), \dots, (\Gamma(t_k),PG_k,ord_k)  &=& compile_{ABGP}(con(pol)) \\
    \end{array} \]%

    where for all product graph nodes $m$ we have $ord_i(m) = ord^A_i(f(m))$, and $PG_i$ and $PG^A_i$ are related by a bisimulation induced by $f$.

>>>>

\begin{defn}
  Assign $ord(m) = ord^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
  Clearly $ord(m) \leq ord(m') \iff m \leq m'$ and $ord(f_{pg}(m)) \leq ord(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
\end{defn}

@@

\begin{thm}
  $compile(con(pol)) = con(compile(pol))$

  \begin{proof} \text{ }

    Suppose that $pol = p_1, \dots, p_n$. Each $p_i$ has the form $(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik})$. Then by evaulating:

    \[ \begin{array}{lcl}
      con(pol) & = & con(p_1,\dots,p_n) \\
               & = & con(p_1), \dots, con(p_n) \\
               & = & con(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k}), \\
               &   & \dots, \\
               &   & con(t_n ~\Path~ r_{n1} ~\Prefer~,\dots, ~\Prefer~ r_{nk}) \\
    \end{array} \]

    For each test $t_i$, if $t_i = pfx$, then we get

    \[ \begin{array}{lcl}
        con({pfx}_{i1} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik}) 
           & = & {pfx}_{i1} ~\Path~ con(r_{i1}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik}) \\
    \end{array} \]

    For each test $t_i$, if $t_i = \$x$, then we get

    \[ \begin{array}{lcl}
        con(\$x_{i} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik}) 
            & = & {pfx}_{i1} ~\Path~ con(r_{i1}) \cap \text{end}(l_{i1}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik}) \cap \text{end}(l_{i1}), \\
            &   & \dots, \\ 
            &   & {pfx}_{ij} ~\Path~ con(r_{i1}) \cap \text{end}(l_{ij}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik}) \cap \text{end}(l_{ij}), \\
            &   & \\
            &   & \text{for each } (pfx_{ij}, l_{ij}) \in \Gamma(x) \\
    \end{array} \]

    Next we compute $compile(con(pol))$:

    \[ \begin{array}{lcl}
        compile(con(pol)) &=& compile_{ABGP}( \\
                          & & ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k} ), \\
                          & & ~~~~ \dots, \\
                          & & ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk} ), \\
                          & & ~~~~ \dots, \\
                          & & ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k} ), \\
                          & & ~~~~ \dots, \\
                          & & ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk} ) \\
                          & & ) \\
    \end{array} \]

    This results in a series of prefixes, product graphs, and orderings of the form: $(pfx_{ij}, PG_{ij}, ord_{ij})$.

    \vspace{1em}
    Similarly, we can compute $compile(pol)$:

    \[ \begin{array}{lcl}
        compile(pol) &=& compile_{ABGP}( \\
                     & & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k} ), \\
                     & & ~~~~ \dots, \\
                     & & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik} ), \\
                     & & ) \\
    \end{array} \]

    This results in a series of prefixes, product graphs, and orderings of the form $(t_i, PG^A_i, ord^A_i)$.

    We know the follwing:

    \begin{itemize}
      \item each $PG^A_i$ and $PG_ij$ are related by a bisimulation induced by $f_{pg}$ for thos product graphs
      \item each $ord^A_i$ and $ord_{ij}$ have the property that $ord^A(f_{pg}(m)) = ord_{ij}(m)$
      \item each $t_i$ has either $t_i = pfx_{ij}$ or $t_i = \$x$ and $\exists l, (pfx_{ij},l) \in \Gamma(x)$.
    \end{itemize}

    %where for all product graph nodes $m$ we have $ord_i(m) = ord^A_i(f(m))$, and $PG_i$ and $PG^A_i$ are related by a bisimulation induced by $f$.
